\chapter*{ABSTRACT}
\addcontentsline{toc}{chapter}{Abstract}

Artificial Intelligence (AI) has emerged as a transformative force across various domains, and its application in economic forecasting and policy design is no exception. With the ability to process vast datasets, identify patterns, and make data-driven predictions, AI offers unparalleled tools for enhancing the accuracy and efficiency of economic analysis.

This report explores the integration of AI techniques—such as machine learning, neural networks, and natural language processing—into the process of economic forecasting and the formulation of public policy. It highlights how AI-driven models can improve decision-making by providing timely and precise forecasts of economic indicators such as GDP, inflation, unemployment rates, and market behavior.

Moreover, the report delves into real-world implementations of AI in governmental and financial institutions and examines the challenges of ethical considerations, data privacy, and model transparency. It also sheds light on the potential of AI to reduce human bias in policy making while offering a dynamic framework to adapt to changing economic conditions.

By analyzing case studies and current research trends, this report provides insights into the future trajectory of AI in economics, aiming to inspire further innovation in data-driven governance and strategic policy development.

\vspace{1.5cm}
\textbf{Keywords:} Artificial Intelligence, Economic Forecasting, Public Policy, Machine Learning, Neural Networks, Natural Language Processing, Data-Driven Decision Making.