\begin{titlepage}
    \justifying
    \centering

    {\LARGE \textbf{ACKNOWLEDGEMENT}}\\[1cm]

    \justifying
    \setlength{\parindent}{1.5em}

    I take this opportunity to thank our college \textbf{Tontadarya College of Engineering, Gadag} for providing us with an opportunity to carry out this project work.

    \vspace{0.4cm}

    I express our gratitude to \textbf{Dr. M M Awati}, Principal, and to \textbf{Dr. Ramesh Badiger}, Associate Professor and HoD of Computer Science and Engineering, Tontadarya College of Engineering, for being a pillar of support and encouraging us in the face of all adversities.

    \vspace{0.4cm}

    I would like to acknowledge the thorough guidance and support extended towards us by \textbf{Prof. Adhokshaja Kulkarni}, Asst. Professor, Department of CSE, Tontadarya College of Engineering, Gadag. His incessant encouragement and valuable technical support have been of immense help. His guidance gave us the environment to enhance our knowledge and skills and to reach the pinnacle with sheer determination, dedication, and hard work.

    \vspace{0.4cm}

    I also want to extend our thanks to the entire faculty and support staff of the Department of Computer Science and Engineering, who have encouraged us throughout the course of the Bachelor's Degree.

    \vspace{0.4cm}

    I want to thank our family for always being there with full support and for providing us with a safe haven to conduct and complete our project. We are ever grateful to them for helping us in these stressful times.

    \vspace{0.4cm}

    Lastly, I want to acknowledge all the helpful insights given to me by all our friends during the course of this technical seminar.

    \vfill

    \begin{flushright}
        \textbf{AZAM MUSTUFA (2TG21CS016)}
    \end{flushright}
\end{titlepage}
